Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-12 journal/content.tex
Improvements on introduction

However, agile methods have originally been designed for use in projects of
limited size \citep{Boehm2005}. It has proven that it may be problematic
to introduce agile practices in large organizations \citep{Dyba2009}.
Nevertheless, the benefits of agile are pursued by large organizations.
% It would also be sociatelly desirable to effectivize large software projects,
% because large projects often have societal influence.

% --> Why is large-scale software development different from smaller scale?
% Agile methods are more difficult to implement in large organizations
% \citep{Dyba2008}.
Compared to small organizations ideal for agile development, large organizations
are characterized by the need of additional coordination. A particular problem
in applying agile to large software organizations is how to handle inter-team
coordination. Large organizations also tend to have additional organizational
units that development must interface with, such as human resources.
Still further, large organizations may cause users and other stakeholders become
distant from development teams.
% The full set of requirements of a large system could be too cumbersome for
% individual teams to manage.
\citet{Boehm2003b} have suggested that sizable organizations should not attempt
to become fully agile.

This thesis presents a study on how large software organizations transform their
way of working towards agile methods. The focus of this study is to explain the
process of transformation, but we have decided to leave out discussion on
measuring the success of the transformation. The study has been performed as a
systematic literature review, drawing the conclusions from previously published
research. Using the systematic literature review method we aim to provide an
objective and broad view on the topic.

@@

Applying agile in large scale has been noted as a current research trend. 
\citep{Freudenberg2010} conducted a survey at the 2010 XP conference,
highlighting ``agile and large projects'' as the one of the hottest research
topics. The trend was continued in the 2013 XP conference, where a research
trends workshop focused specifically on large scale agile development. The
viewpoint on introduction of agile methods was highlighted in the workshop
\citep{Dingsoyr2013a}.

Research on agile software development is accumulating and maturing, and has
provided ground for performing systematic literature reviews
\citep{Dyba2008,Jalali2012,Senapathi2013,Kaisti2013}. Still, the area of large
scale agile development has not yet been studied through secondary studies. In
the mean time numerous studies discussing agile adoption have been published.
This setting provides an opportunity to aggregate the findings of primary
studies, and thereby fill a gap in research on large scale agile adoption.

>>>>

However, agile methods have originally been designed for use in projects of
limited size \citep{Boehm2005}. It has proven that agile methods are more
difficult to implement in large organizations \citep{Dyba2009}.
Still, regardless of the challenges that large scale agile adoption poses, the
benefits of agile are pursued by large organizations.
% It would also be sociatelly desirable to effectivize large software projects,
% because large projects often have societal influence.

% Agile methods are more difficult to implement in large organizations
% \citep{Dyba2008}.
Compared to small organizations ideal for agile development, large organizations
are characterized by the need of additional coordination. A particular problem
in applying agile to large software organizations is how to handle inter-team
coordination. Large organizations also tend to have additional organizational
units that development must interface with, such as human resources.
Still further, large organizations may cause users and other stakeholders become
distant from development teams.
Regardless of these known problems there is an industry trend of large scale
agile adoptions. An additional challenge is the lack of research on how to
introduce agile methods to large organizations.
% The full set of requirements of a large system could be too cumbersome for
% individual teams to manage.
% \citet{Boehm2003b} have suggested that sizable organizations should not
% attempt to become fully agile.

This thesis presents a study on how large software organizations transform their
way of working towards agile methods. The focus of this study is to explain the
process of transformation, but we have decided to leave out discussion on
measuring the success of the transformation. The study has been implemented as a
systematic literature review, drawing the conclusions from previously published
research. Using the systematic literature review method we aim to provide an
objective and broad view on the topic.

@@

In research large scale agile development is still a new area, although
it is gaining interest.
\citet{Freudenberg2010} conducted a survey at the 2010 XP conference,
highlighting ``agile and large projects'' as the one of the hottest research
topics. The trend was continued in the 2013 XP conference, where a research
trends workshop focused specifically on large scale agile development. The
viewpoint on introduction of agile methods was one of the highlighted themes in
the workshop \citep{Dingsoyr2013a}.

Research on agile software development is accumulating and maturing, and has
provided ground for performing systematic literature reviews
\citep{Dyba2008,Jalali2012,Senapathi2013,Kaisti2013}. Still, the area of large
scale agile development has not yet been studied through secondary studies. In
the mean time numerous reports discussing agile adoption have been published.
This setting provides an opportunity to aggregate the findings of primary
studies, and thereby fill a gap in research on large scale agile adoption.
